---
title: "Project 1"
output: html_notebook
---
Project 1 for DATA 607

Wiktoria Gnojek 

The initial link to the data set can be found here; https://bbhosted.cuny.edu/bbcswebdav/pid-59650551-dt-content-rid-462255833_1/courses/SPS01_DATA_607_002_1219_1/SPS01_DATA_607_002_1219_1_ImportedContent_20210819013518/SPS01_DATA_607_001_1219_1_ImportedContent_20210818092307/SPS01_DATA_607_02_1202_1_ImportedContent_20200126080334/tournamentinfo.txt

I've also exported the txt file to a github page, in case the link above isn't accessible for everyone; https://github.com/WiktoriaGnojek/tournamentinfo/blob/main/tournamentinfo.txt
```{r}
library(tidyverse)
library(readr)
library(stringr)
```
Framing the Problem

First, we'll begin by exporting the data to this R markdown. We want to create an R markdown file that can be stored as a CSV with appropriate headings and average pre-chess ratings. 
```{r}
tournamentinfo <- read.csv("https://raw.githubusercontent.com/WiktoriaGnojek/tournamentinfo/main/tournamentinfo.txt",header = FALSE)
tournamentinfo
```
Processing the Data 

To begin the clean up process, we will be getting rid of the initial first lines of the data set. These include the headings. 
```{r}
noheadings <- tournamentinfo[-c(1:3),]
head(noheadings)
```
Extracting the Data 

Each players information is split into two rows, we want to extract the two rows so that it is easier to reference. 
```{r}
player_info <- noheadings[seq(2,length(noheadings),3)]
head(player_info)
match_info <- noheadings[seq(3,length(noheadings),3)]
head(match_info)
```
Exploring the Data and Creating Our Own Table

Now that we extracted the data, we will begin creating and solving the initial project question. First we will create a customized data set with the following info; Player’s Name, Player’s State, Total Number of Points, and Player’s Pre-Rating. At this point we are using string extractions, you can find the information on this in the R for Data Science book, chapter 14.

We are also using regex expressions, as a guide I used this cheatsheet; https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_strings.pdf
```{r}
library(stringr)
Player_Name <- str_extract(player_info, "(\\w+\\s){2,3}") 
Player_State <- str_extract(match_info,"\\w\\w") 
Total_Num_Of_Points <- str_extract(player_info,"\\d.\\d") 
Players_Pre_Rating <- as.numeric(str_extract(str_extract(match_info, "\\D\\d{3,4}\\D"), "\\d+")) 
```
Finally, we can find the "Average Pre Chess Rating of Opponents".

First, we have to extract opponent data. This data is found in the first row of our split, and in the initial data set it is under the rounds per player. 
```{r}
opponent_data <- str_extract_all(player_info, "\\d+\\|")
opponent_data <- str_extract_all(opponent_data, "\\d+")
head(opponent_data)
```
Next, we calculate average pre chess ratings of opponents. 
```{r}
Opponent_Pre_Ave_Rating <- c()
for (i in c(1:length(opponent_data))) {
  Opponent_Pre_Ave_Rating[i] <- round(mean(Players_Pre_Rating[as.numeric(opponent_data[[i]])]),0)
}
Opponent_Pre_Ave_Rating 
```
Combining All in One Table 
```{r}
df <- data.frame(Player_Name,Player_State,Total_Num_Of_Points,Players_Pre_Rating,Opponent_Pre_Ave_Rating)
df
```
```{r}
write_csv(df, "tournament.csv")
```




